Automatic prostate cancer detection through \acs*{dce}-\acs*{mri} images: all you need is a good normalization

### 2016-08-27 02_methods/methods.tex
Added the figures missing
symbol

\begin{figure*}
  \centering
  \hspace*{\fill}
  \subfigure[]{\label{subfig:pathhist}\includegraphics[width=1\textwidth]{02_methods/figures/heatmaprep.pdf}} \hfill
  \hspace*{\fill}
  \\
  \hspace*{\fill}
  \subfigure[]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1_annotated.pdf}} \hfill
  \subfigure[]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2.pdf}} \hfill
  \hspace*{\fill}
  \caption{\subref{subfig:pathhist} Illustration of the heatmap representation: all \ac*{pdf}s of the prostate gland are concatenated together to build an heatmap; \subref{subfig:pat1}-\subref{subfig:pat2} Illustration of inter-patient variations (i.e., $\Delta_i$, $\Delta_t$, and $\sigma_i$) \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
  \label{fig:heatmap}
\end{figure*}

In \ac{dce}-\ac{mri}, the intensity \ac{pdf} of prostate gland does not follow a unique type of distribution such as Rician or Gaussian distribution, as shown in Fig.\,\ref{subfig:pathhist}.
Indeed, the inter-patient variations are more complex due to the temporal acquisition.
A better representation to observe these variations is to represent the intensity \ac{pdf} of the \ac{dce}-\ac{mri} data over time using a heatmap representation as shown in Fig.\,\ref{subfig:pathhist}.
Analyzing this heatmap representation across patients (see Fig.\,\ref{subfig:pat2}), the following variations are highlighted:
(i) an intensity offset $\Delta_i$ of the \ac{pdf} peak at pre-contrast,
(ii) a time offset $\Delta_t$ depending of the contrast agent arrival, and
(iii) a change of scale $\sigma_i$ related to the signal enhancement.
Therefore, our normalization method should attenuate all these variations and be performed globally across the different time sequence rather than for each independent sequence.

>>>>

\begin{figure*}
  \centering
  \hspace*{\fill}
  \subfigure[]{\label{subfig:pathhist}\includegraphics[width=1\textwidth]{02_methods/figures/heatmaprep.pdf}} \hfill
  \hspace*{\fill}
  \\
  \hspace*{\fill}
  \subfigure[]{\label{subfig:pat1}\includegraphics[width=.49\textwidth]{02_methods/figures/pat1_annotated.pdf}} \hfill
  \subfigure[]{\label{subfig:pat2}\includegraphics[width=.49\textwidth]{02_methods/figures/pat2_annotated.pdf}} \hfill
  \hspace*{\fill}
  \caption{\subref{subfig:pathhist} Illustration of the heatmap representation: all \ac*{pdf}s of the prostate gland are concatenated together to build an heatmap; \subref{subfig:pat1}-\subref{subfig:pat2} Illustration of inter-patient variations (i.e., $\Delta_i$, $\Delta_t$, and $\alpha_i$) \acs*{pdf} over time of two patients in a \ac{dce}-\ac{mri}.}
  \label{fig:heatmap}
\end{figure*}

In \ac{dce}-\ac{mri}, the intensity \ac{pdf} of prostate gland does not follow a unique type of distribution such as Rician or Gaussian distribution, as shown in Fig.\,\ref{subfig:pathhist}.
Indeed, the inter-patient variations are more complex due to the temporal acquisition.
A better representation to observe these variations is to represent the intensity \ac{pdf} of the \ac{dce}-\ac{mri} data over time using a heatmap representation as shown in Fig.\,\ref{subfig:pathhist}.
Analyzing this heatmap representation across patients (see Fig.\,\ref{subfig:pat2}), the following variations are highlighted:
(i) an intensity offset $\Delta_i$ of the \ac{pdf} peak at pre-contrast,
(ii) a time offset $\Delta_t$ depending of the contrast agent arrival, and
(iii) a change of scale $\alpha_i$ related to the signal enhancement.
Therefore, our normalization method should attenuate all these variations and be performed globally across the different time sequence rather than for each independent sequence.
